\documentclass[11pt]{article}

% Page + typography
\usepackage[margin=1.25in]{geometry}
\usepackage{microtype}
\usepackage{setspace}
\usepackage{parskip} % modern paragraph spacing (no indents)
\usepackage[none]{hyphenat} % prevent word hyphenation (e.g. "distri-")

% Paragraph spacing (used as the "after heading" gap too)
\setlength{\parskip}{1em}
\setlength{\parindent}{0pt}

% Keep justified text readable even without hyphenation
\hyphenpenalty=10000
\exhyphenpenalty=10000
\emergencystretch=1em

% Fonts
% - Use Helvetica (sans) for a clean, modern spec feel
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage{helvet}
  \renewcommand{\familydefault}{\sfdefault}
\else
  \usepackage{fontspec}
  % Use a font name XeTeX can reliably resolve via CoreText.
  \IfFontExistsTF{Helvetica}
    {\setmainfont{Helvetica}}
    {\setmainfont{TeX Gyre Heros}}
\fi

% Links
\usepackage[colorlinks=true, urlcolor=blue!60!black]{hyperref}
\usepackage{xcolor}
\usepackage{graphicx}

% Section styling (clean, spec-like)
\usepackage{titlesec}
\usepackage{titling}
\titleformat{\section}
  {\normalfont\bfseries\large\color{black!80}}
  {\thesection.}{0.25em}{}
\titlespacing*{\section}{0pt}{2.5em}{\parskip}

\setstretch{1.12}

\title{personal token}
\author{}
\date{}

\begin{document}
\thispagestyle{plain}

\begin{flushleft}
{\LARGE\mdseries\color{black!85} \scalebox{1.25}{\thetitle}\par}
\vspace{0.75em}
{\normalsize\normalfont\emph{a primitive for sharing lifetime upside}}
\end{flushleft}
\vspace{0.35in}

\section{Problem}

We can incentivize help for specific ideas by sharing equity in companies.

But we lack a similar mechanism to incentivize help at the level of a person's life.

As a result, many worthwhile explorations never begin or receive the help they need.

\section{Personal token}

A personal token represents the economic value a person creates over the course of their life through activities characterized by extreme upside potential, power-law outcome distributions, and superlinear growth.

A personal token has shares. Each share represents a proportional claim on the token owner's realized capital gains from equity in companies, personal tokens, and similar structures.

\section{Valuation}

A personal token is valued at the level of a life, not a single idea.

As with other financial assets, valuation is based on expectations of future outcomes rather than the current state. A personal token may therefore be valued well above the individual's present holdings, proportional to belief in their potential.

\section{Collaboration}

By sharing equity in their personal tokens, individuals can incentivize collaboration at the level of their lives, beyond any specific idea or venture.

This enables support for exploration, learning, and preparation that does not depend on the success of any single idea, including phases before concrete ideas exist.

\section{Control}

Shareholding in a personal token does not give control over the token owner's life or decision making.

Personal token shares are not freely tradable assets. The token owner retains control over who may hold equity in their token.

Token owners may issue new shares at any time, diluting existing shareholders. There are no pro rata rights: token owners may refuse shareholders from purchasing future shares.

Secondary sales require the token owner's approval.

\section{Safety}

Token owners can divorce themselves from shareholders by buying back equity at the current fair market value.

The token does not directly expose the token owner's equity holdings to shareholder claims, or constrain how the owner creates value.

A personal token is strictly scoped to upside from realized capital gains. In the worst case, the token owner owes nothing.

\section{Reputation}

The state of a personal token is public, incentivizing token owners to be fair. Unfairness jeopardizes help from current and future collaborators.

What is fair is determined by the market.

\section{Growth}

Token owners can reinvest realized capital gains - that would otherwise be distributed to shareholders - back into themselves to fuel growth.

Capital gains are reinvested while growth is expected, and distributed to shareholders when it is not, based on ongoing shareholder voting.

\section{Liquidity}

Shareholders will primarily realize value through secondary sales, rather than through distributions, as capital gains are typically reinvested to fuel growth.

At the discretion of the token owner, specific subsets of shares may be made transferable through permissioned, limited liquidity pools, which may be modified or revoked at any time. These pools enable liquidity and price discovery without creating a public or permissionless market.

Secondary transfers route a small royalty back to the token owner, aligning incentives to enable and sustain liquidity over time.

\section{Death}

At death, a token owner's assets are liquidated and capital gains distributed to shareholders, settling any gains that were reinvested rather than distributed.

\vspace{2em}
\noindent\rule{\linewidth}{0.4pt}
\vspace{1.25em}

\noindent\url{https://onroot.net}

\noindent--- homan

\end{document}